A Network Approach to Social Distinction

### 2025-11-10 manuscript.tex

\begin{document}
\title{Network Origins of Social Distinction}
\author[1]{Author Isaac Jilbert\thanks{isaac.jilbert@gmail.com}}
\author[1]{Omar Lizardo\thanks{olizardo@soc.ucla.edu}}
\affil[1]{Department of Sociology, UCLA}

@@

\newpage
\begin{abstract}	
This paper introduces the concept of network \textit{distinction} and develops a relational metric that captures it. The metric is theoretically inspired by Bourdieu's theory of agonistic competition for distinction in social fields, where other actors and their actions provide opportunities and constraints to maximize social positioning. The basic idea behind the network metric of distinction is to subtract the \textit{autonomy} of each actor within the network from their \textit{constraint}, such that highly autonomous (and therefore less constrained) actors have more distinction. Autonomy is given by the focal actor's Eigenvector Centrality score (recording connections to well-placed others), and constraint is defined by the average Eigenvector Centrality score of each actor's neighbors in a hypothetical network where the focal actor is removed (indicating how others would benefit from that actor's exiting the network). A scalar is then applied to create mathematical and sociological equivalence between autonomy and constraint. The resulting node-level measures create a measure of \textit{distinction}, where the uniqueness of an actor's relations is more heavily rewarded than under the standard Eigenvector Centrality score. We analyze two classic datasets, Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club, to demonstrate that the observed actions of the agents involved are consistent with the maximization of distinction. We close by outlining how the resulting distinction measure can be used to both forecast network transformations and anticipate competitive changes resulting from external network shocks.    
\end{abstract}

\newpage
\section{Distinction Beyond Taste}
Popular within cultural sociology, the concept of distinction has generated a rich body of literature aimed at explaining cultural differentiation within social fields. From this perspective, the pursuit of distinction, as the expression of an actor's status and uniqueness, is an end in itself, providing the basic motivation for action \citep{martin2003field}. The question of cultural distinction is often treated empirically as a matter of the deference given to symbolic forms of differentiation enacted by designated institutional authorities \citep{bourdieu1984distinction}.

In this last respect, the more encompassing notion of \textit{social} distinction, implying an actor's embeddedness in a relational field \citep{erikson2013formalist-400, fuhse2021social-9cb}, is often measured as the shadow counterpart of cultural distinction or collapsed into the concept of status more generally \citep{podolny2010status-1a6}. This approach overlooks questions of how network constraints produced by other agents impact the capacity of actors to be distinct. A generalized, measured ordering of social distinction that is derivative from a network of concrete social relations would give Bourdieu's generalized conception of distinction a broader methodological base from which to conduct empirical analysis.

\subsection{What is Distinction?}
Bourdieu was primarily interested in the competition among actors for positions within the hierarchy implied by the field \citep{anheier1995forms, bourdieu1993field-8ad}. Bourdieu defined the field as a social space where actors operate within socially negotiated boundaries that arbitrate relevant competitive claims over position \citep{bourdieu1996rules-393}. In interplay with the field, individuals develop a habitus of embodied dispositions, expressed as cognitive ease with particular types of settings, objects, and performances. An actor's position in the field influences their habitus. Similarly, their habitus determines their future possibilities within the field, while also shaping the opportunities available to others in the field. Actors compete for positions in the field via various forms of capital or resources that are socially agreed upon as desirable within a field \citep{martin2003field}, thereby facilitating the formation of connections that both order and reflect the hierarchy of the field. The interaction of the desirability and uniqueness of the capitals possessed by an individual determines their place in the field's positional hierarchy.

Bourdieu \citeyearpar{bourdieu1984distinction} most famously used the conceptualization of distinction to explain the persistence of the relationship between class and cultural hierarchies. Cultural elites in France distinguished themselves from their inferiors by adopting differentiated cultural practices that had undergone a process of consecration, which set them apart from the common. There is a strong correlation between those in the position of cultural and economic elites. Still, such a correlation is not guaranteed at the individual level, even if it is relevant at the field level.   
While largely a concept used by those who research cultural practices, the pursuit of distinction is a general expression of the interaction between status and uniqueness within a field of positions \citep{anheier1995forms}. For example, while cultural practices may be a marker of difference, the absence of association with others outside the milieu is also a matter of agency within the milieu, a question of the constraints imposed by the set of relationships within which the actor is embedded. For Bourdieu, the struggle for position in a field was a product of a field of action and a field of forces \citep{martin2003field}. The field of action refers to the agency of actors actively advancing their interests. In contrast, the field of forces describes the counteracting pressures faced by the other participants whose interests would be upset by positional transformations.

In relation to theory, network status is another name for \textit{influence} \citep{friedkin1991theoretical}, and uniqueness for \textit{autonomy} in a social environment \citep{burt1980autonomy}. Translated into network terms, Bourdieu's field of action can be understood as the status hierarchy of the network, while the field of struggle reflects the constraints that neighbors impose on an actor. An actor with high influence is well-connected to others who can be mobilized for effective action. An actor with high autonomy is not constrained by their pattern connections or forced into action by them \citep{burt76}. We often use context-specific words to denote position in the hierarchy and ability to act within that hierarchy. Nevertheless, we use ``status" and ``autonomy" below as general terms to describe the ability of actors to take action versus the level of imposition from the forces of constraint.

In developing a broader understanding and measure of social distinction, actor-level incentives and structural impediments to action become apparent. When we understand the underlying motivation that actors have to proactively reshape their network connections to achieve more distinct positions, historical patterns of network change can be better accounted for and, in some cases, even properly forecasted.

\subsection{Position as the Relational Basis for a Distinction Measure}
Bourdieu's separation of distinction into habitus and position is not a sociological problem in itself, but rather creates the analytical challenge of how an actor's network position generates dispositions and how these dispositions, in turn, create opportunities for network mobility. Both dispositions and positions are fundamentally relational outcomes in sociological terms; however, when creating a network measure of distinction, only the relational basis of position can be considered.

However, to the extent that position and habitus reflect each other through their symbiotic fabrication, the ability to empirically capture only one of the two components is sufficiently accurate to measure a social system's distinction hierarchy with confidence over a short window of time. Actors should not hold a network position that does not align with their habitus, and their current habitus and social position determine their ability to radically change positions. If the transformation of habitus is a stepwise interplay with positional movement that unfolds over time, the measure becomes less informative if it captures networks over extended periods. However, even over long periods, this theoretical collapse, which permits a network-measured methodological shortcut, may still be adequate in a moderately stable social environment.

To establish a firm theoretical foundation for the measure of distinction, it is first essential to make explicit the relationship between empirical data and social theory that forms the basis of social network analysis. Network measures are fundamentally based on the idea that researchers are capturing a relationship between two objects in some way. A tie between two nodes captures, in some way, their connection, however it is defined. Such connections can be broadly classified as mutual, in the case where the relationship quality is equal in both directions, or directional, in the case where the qualities are unequal. In the absence of direct measurement of qualities, however, many networks are measured as consisting of mutual ties. However, even in the case of networks composed of only mutual ties, hierarchy can still be assessed from the pattern of relationships. In such networks, we can still rank the direction of power and deference through the absence of ties between lower and higher nodes. For example, in an organizational pyramid, we can detect the CEO by observing the presence of ties with vice presidents and the absence of ties with middle management and production workers. We can do this through the measurement of a node's network status.

The first aspect of social distinction is \textit{status}. Status refers to the internal stratification of all network members, along with the connections of deference and obligation. In the case of politics, status refers to the ability to access those who themselves have higher levels of access, with those most central to the access network having the authority to make decisions. This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972factoring-03e}. Status is higher for actors when the people they are connected to are themselves influential, and accessibility is merely a political reframe of the context. The internal stratification of individuals is determined by who has greater connections to those with even greater connections, with those having few connections to other important people being at the bottom of the hierarchy \citep{bonacich1972factoring-03e}.

The second aspect of social distinction is \textit{autonomy}, which is the absence of network constraint \citep{burt1980autonomy}. Being structurally unique minimizes the social constraints placed on an individual. The tighter the interconnections of the group, the more its pressures constrain the individual. In politics, this aspect of distinction takes the form of constraint. When an actor is one of many densely interconnected individuals, their ability to act contrary to their networked group is greatly weakened. However, when one is only a weakly dependent and connected member of a group, they have a greater ability to operate independently. Their ability to act is a source of distinction as they are able to take independent action. The question of structural uniqueness and autonomy is the same underlying consideration as captured by measures of path centrality. The more critical one is to bridge connections between individuals within a network, the greater one's importance, and the lower their constraint \citep{burt1995structural-5e8}.

\citet[1263-4]{padgett1993robust} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions. Cosimo de Medici, acting as a broker between two antagonistic groups, was constrained in the actions he could take because strong actions favoring one side would upset the other side. However, such a constraint was not an issue because Medici’s interests were in perpetuating his central role as broker, and, as the only source of interest, he was able to maintain the position. With regard to conceptualizing distinction, the theory of robust action puts forward that those at the center of political networks, as long as their interests derive solely from maintaining that position, engage in moderate strategies that do not overly antagonize either side. The decisions are based on ensuring their continued position at the center of the network.

The interaction of influence and autonomy combines to create an actor’s overall distinction in the network. The combination of influence and autonomy results in capacity, and the social reward for this capacity is distinction. An increase in one aspect can often, but not necessarily, lead to a decrease in the other. For example, a connection with someone with high accessibility can lead to a decrease in one’s autonomy, and new access comes with new constraints. However, the trade-off can maximize one’s overall distinction, so there are gains from the connection. Without such gains, the connection would not be formed.

\section{A Generalized Measure of Network Distinction}
In this section, we present our measure of distinction centrality, which incorporates a scalar adjustment factor to mitigate arbitrary scaling issues. We also indicate the availability of an \textit{R} custom function to facilitate the easy implementation of the measure in further work.

@@

Formalizing the interaction between status and uniqueness allows for a measure of network distinction. Distinction as a theoretical concept is composed of status mediated by autonomy. A distinction measure can reflect this by considering an actor's status and then discounting it by the counterfactual status of their neighbors when the focal actor is absent from the network. The more reliant an actor's neighbors are on the actor for their status, the lower the focal actor's ability to exert influence over them, and thus the lower their distinction. In other words, autonomy is determined by how much one's neighbors rely on you to maintain their advantageous position in the network.

@@

%brokerage and structural folds Figure 4
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
            \caption{Structural Fold (4-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
            \caption{Structural Fold (5-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
            \caption{Two-Connected}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
            \caption{Circle Weld}
            \label{fig:circleweld}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker3.png}
            \caption{Brokerage Mediated (3-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \label{fig:struct-fold}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker4.png}
            \caption{Brokerage Mediated (4-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
            \caption{Tree with 2 Branches, 2 Leaves}
            \label{fig:treemediator2}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
            \caption{Tree with 2 Branches, 3 Leaves}
            \label{fig:treemediator3}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
            \caption{Tree with 2 Branches, 2 Leaves, 1 Long Tie}
            \label{fig:treemediatorlong2}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
            \caption{Tree with 2 Branches, 3 Leaves, 1 Long Tie}
            \label{fig:treemediatorlong3}
    \end{subfigure}
    \caption{Comparison of betweenness brokerage and a structural fold goes here}
\end{figure}

@@

%%% FIGURE 5 KITE GRAPHS
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Three-Clique/Wheel}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
            \caption{Six-Node Wheel}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Six-Clique}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
            \caption{Ten-Clique}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique.png}
            \caption{Three Levels of Hierarchy}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-star.png}
            \caption{Kite Connects to Highest Distinction Node}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-clique.png}
            \caption{Kite Connects to Moderate Distinction Node}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-peri.png}
            \caption{Kite Connects to Lowest Distinction Node}
            \label{fig:circleweld}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
            \caption{Kite Connects to Moderate Distinction Node}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
            \caption{Kite Connects to Lowest Distinction Node}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
            \caption{HOLD}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
            \caption{HOLD}
            \label{fig:sf}
    \end{subfigure} 
    \caption{Comparison of kite graphs with varying parameters}
\end{figure}

@@

\subsection{Capital Conversion as Network Integration of Fields}
One of the problems with the relationship between multiple fields is how capital might be converted between fields. The ``rate'' between fields has always been a matter of confusion because it is difficult to quantify. Yet, it is an essential feature of an individual's navigation between the positional hierarchies of various fields. Seeking to convert a distinct position from one field to a better position in another is a critical strategy in the overall positional portfolio of agents.

>>>>

\begin{document}
\title{A Network Approach to Social Distinction}
\author[1]{Author Isaac Jilbert\thanks{isaac.jilbert@gmail.com}}
\author[1]{Omar Lizardo\thanks{olizardo@soc.ucla.edu}}
\affil[1]{Department of Sociology, UCLA}

@@

\newpage
\begin{abstract}	
This paper introduces the concept of network \textit{distinction} and develops a relational metric to capture it. The metric is theoretically inspired by Bourdieu's theory of agonistic competition for distinction in social fields, in which other actors and their actions provide opportunities and constraints for maximizing social positioning. The basic idea behind the network metric of distinction is to subtract each actor's \textit{autonomy} from their \textit{constraint}, so that highly autonomous (and therefore less constrained) actors have greater distinction. Autonomy is measured by the focal actor's Eigenvector Centrality score (indicating connections to well-placed others), and constraint is defined by the average Eigenvector Centrality score of each actor's neighbors in a hypothetical network in which the focal actor is removed (indicating how others would benefit from that actor's exit from the network). A scalar is then applied to create mathematical and sociological equivalence between autonomy and constraint. The resulting node-level measures yield a measure of \textit{distinction}, in which the uniqueness of an actor's relations is more heavily rewarded than under the standard Eigenvector Centrality score. We analyze two classic datasets, Padgett and Ansell's \citeyearpar{padgett1993robust} Medici Network and Zachary's \citeyearpar{zachary1977information} Karate Club, to show that the observed actions of the agents involved are consistent with the maximization of distinction. We close by outlining how the resulting distinction measure can be used to both forecast network transformations and anticipate competitive changes resulting from external network shocks.    
\end{abstract}

\newpage
\section{Distinction Beyond Taste}
Popular within cultural sociology, the concept of distinction has generated a rich body of literature aimed at explaining cultural differentiation within social fields. From this perspective, the pursuit of distinction, as the expression of an actor's status and uniqueness, is an end in itself, providing the basic motivation for action \citep{martin2003field}. The question of cultural distinction is often treated empirically as a matter of the deference given to symbolic forms of differentiation enacted by designated institutional authorities \citep{bourdieu1984distinction}. In this last respect, the more encompassing notion of \textit{social} distinction, implying an actor's embeddedness in a relational field \citep{erikson2013formalist-400, fuhse2021social-9cb}, is often measured as the shadow counterpart of cultural distinction or collapsed into the concept of status more generally \citep{podolny2010status-1a6}. This approach overlooks how network constraints imposed by other agents affect actors' capacity to be distinct. A generalized, measured ordering of social distinction, derived from a network of concrete social relations, would give Bourdieu's conception a broader methodological base for empirical analysis.

\subsection{What is Distinction?}
Bourdieu was primarily interested in the competition among actors for positions within the hierarchy implied by the field \citep{anheier1995forms, bourdieu1993field-8ad}. Bourdieu defined the field as a social space where actors operate within socially negotiated boundaries that arbitrate relevant competitive claims over position \citep{bourdieu1996rules-393}. In interplay with the field, individuals develop a habitus of embodied dispositions, expressed as cognitive ease with particular types of settings, objects, and performances. An actor's position in the field influences their habitus. Similarly, their habitus determines their future possibilities within the field while also shaping the opportunities available to others. Actors compete for positions in the field via various forms of capital or resources that are socially agreed upon as desirable within the field \citep{martin2003field}, thereby facilitating the formation of connections that both order and reflect the field's hierarchy. The interaction between an individual's desirability and the uniqueness of their capital determines their place in the field's positional hierarchy.

Bourdieu \citeyearpar{bourdieu1984distinction} most famously used the conceptualization of distinction to explain the persistence of the relationship between class and cultural hierarchies. Cultural elites in France distinguished themselves from their inferiors by adopting practices that had undergone a process of consecration, thereby setting them apart from the common. There is a strong correlation between those in the position of cultural and economic elites. Still, such a correlation is not guaranteed at the individual level, even if it is relevant at the field level.

While largely a concept used by those who research cultural practices, the pursuit of distinction is a general expression of the interaction between status and uniqueness within a field of positions \citep{anheier1995forms}. For example, while cultural practices may be a marker of difference, the absence of association with others outside the milieu is also a matter of agency within the milieu, a question of the constraints imposed by the set of relationships within which the actor is embedded. For Bourdieu, the struggle for position in a field was a product of a field of action and a field of forces \citep{martin2003field}. The field of action refers to the agency of actors actively advancing their interests. In contrast, the field of forces describes the counteracting pressures faced by the other participants whose interests would be disrupted by the actor's positional transformations.

In relation to theory, network status is another name for \textit{influence} \citep{friedkin1991theoretical}, and uniqueness for \textit{autonomy} in a social environment \citep{burt1980autonomy}. Translated into network terms, Bourdieu's field of action can be understood as the network's status hierarchy, while the field of struggle reflects the constraints neighbors impose on an actor. An actor with high influence is well-connected to others who can be mobilized for effective action. An actor with high autonomy is not constrained by their pattern connections or forced into action by them \citep{burt76}. We often use context-specific words to denote position in the hierarchy and the ability to act within it. Nevertheless, we use ``status" and ``autonomy" below as general terms to describe the actors' ability to maneuver for better positioning against the level of constraint imposed by external forces, which usually means other actors and their relations.

In developing a broader understanding and measure of social distinction, the interplay between actor-level incentives and structural impediments to action becomes apparent. When we understand the underlying motivations that drive actors to proactively reshape their network connections to achieve more distinct positions, historical patterns of network change can be better accounted for and, in some cases, even predicted.

\subsection{Position as the Relational Basis for a Distinction Measure}
Bourdieu's separation of distinction into habitus and position is not a sociological problem in itself; rather, it poses the analytical challenge of how an actor's network position generates dispositions, and how these dispositions, in turn, create opportunities for network mobility. Both dispositions and positions are fundamentally relational outcomes in sociological terms; however, when developing a network measure of distinction, only the relational basis of position can be considered.

However, to the extent that position and habitus reflect each other through their symbiotic connection, empirically capturing only one of the two components is sufficient to measure a social system's distinction hierarchy with confidence over a short time window. Actors should not hold a network position that does not align with their habitus, and their current habitus and social position determine their ability to radically change positions. If the transformation of habitus is a stepwise interplay with positional movement that unfolds over time, the measure becomes less informative if it captures networks over extended periods. However, even over long periods, this theoretical collapse, which permits a network-measured methodological shortcut, may still be adequate in a moderately stable social environment.

To establish a firm theoretical foundation for the measure of distinction, it is first essential to make explicit the relationship between empirical data and social theory that underlies social network analysis. Network measures are fundamentally based on the idea that researchers are capturing a relationship between two agents. A tie between two nodes captures, in some way, their connection, however it is defined. Such connections can be broadly classified as mutual, when the relationship quality is equal in both directions, or directional, when the qualities are unequal. In the absence of direct measurement of qualities, however, many networks are measured as consisting of mutual ties. However, even in networks composed solely of mutual relations, hierarchy can still be assessed from the pattern of relationships. In such networks, we can still rank the direction of power and deference through the absence of ties between lower and higher nodes. For example, in an organizational pyramid, we can detect the CEO by observing the presence of relations with vice presidents and the absence of ties with middle management and production workers. We can do this by measuring a node's network status.

The first aspect of social distinction is \textit{status}. Status refers to the internal stratification of all network members, along with the connections of deference and obligation. In politics, status refers to the ability to access those who themselves have greater access, with those most central to the access network having the authority to make decisions. This can be captured traditionally by measures of status such as eigenvector centrality \citep{bonacich1972factoring-03e}. Status is higher for actors when the people they are connected to are themselves influential, and accessibility is merely a political reframe of the context. The internal stratification of individuals is determined by who has stronger connections to those with even stronger connections, with those having few connections to other important people at the bottom of the hierarchy \citep{bonacich1972factoring-03e}.

The second aspect of social distinction is \textit{autonomy}, which is the absence of network constraint \citep{burt1980autonomy}. Being structurally unique minimizes the social constraints placed on an individual. The tighter the group's interconnections, the more its pressures constrain the individual. In politics, this aspect of distinction takes the form of constraint. When an actor is one of many densely interconnected individuals, their ability to act contrary to their group is significantly weakened. However, when one is only a weakly dependent and connected member of a group, they have a greater ability to operate independently. Their ability to act is a source of distinction, as they can take independent action. The question of structural uniqueness and autonomy is the same underlying consideration as captured by measures of path centrality. The more critical one is to bridge connections between individuals within a network, the greater one's importance, and the lower their constraint \citep{burt1995structural-5e8}.

\citet[1263-4]{padgett1993robust} were the first to bring attention to how the cohesion of those around a broker can structure their own decisions. Cosimo de Medici, acting as a broker between two antagonistic groups, was constrained in the actions he could take because decisive steps favoring one side would upset the other. However, this constraint was not an issue because Medici’s interests lay in perpetuating his central role as broker, and, as the only source of interest, he was able to maintain his position. When conceptualizing distinction, the theory of robust action puts forward that those at the center of political networks, as long as their interests derive solely from maintaining that position, engage in moderate strategies that do not overly antagonize either side. The decisions are based on ensuring their continued position at the center of the network.

The interaction between influence and autonomy creates an actor’s overall distinction in the network. The combination of influence and autonomy results in capacity, and the social reward for this capacity is distinction. An increase in one aspect can often, but not necessarily, lead to a decrease in the other. For example, a connection with someone with high accessibility can lead to a reduction of one’s autonomy, and new access comes with new constraints. However, the trade-off can maximize one’s overall distinction, so there are gains from the connection. Without such gains, the connection would not be formed.

\section{A Generalized Measure of Network Distinction}
In this section, we present our measure of distinction centrality, which incorporates a scalar adjustment factor to mitigate issues arising from arbitrary scaling. We also indicate the availability of an \textit{R} custom function to facilitate the easy implementation of the measure in further work.

@@

Formalizing the interaction between status and uniqueness allows for a measure of network distinction. Distinction as a theoretical concept is composed of status mediated by autonomy. A distinction measure can reflect this by considering an actor's status and then discounting it by the counterfactual status of their neighbors when the focal actor is absent from the network. The more reliant an actor's neighbors are on the focal actor for their status, the lower the focal actor's ability to exert influence over them, and thus the lower the focal actor's distinction. In other words, autonomy is determined by how much one's neighbors rely on you to maintain their advantageous position in the network.

@@

%brokerage and structural folds Figure 4
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
            \caption{Structural Fold (4-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
            \caption{Structural Fold (5-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
            \caption{Two-Connected}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
            \caption{Circle Weld}
            \label{fig:circleweld}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker3.png}
            \caption{Brokerage Mediated (3-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \label{fig:struct-fold}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker4.png}
            \caption{Brokerage Mediated (4-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
            \caption{Tree with 2 Branches, 2 Leaves}
            \label{fig:treemediator2}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
            \caption{Tree with 2 Branches, 3 Leaves}
            \label{fig:treemediator3}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
            \caption{Tree with 2 Branches, 2 Leaves, 1 Long Tie}
            \label{fig:treemediatorlong2}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
            \caption{Tree with 2 Branches, 3 Leaves, 1 Long Tie}
            \label{fig:treemediatorlong3}
    \end{subfigure}
    \caption{Comparison of betweenness brokerage and a structural folds Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

@@

%%% FIGURE 5 KITE GRAPHS
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Three-Clique/Wheel}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-edge.png}
            \caption{Six-Node Circle}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Six-Clique}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
            \caption{Ten-Clique}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique.png}
            \caption{Three Levels of Hierarchy}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-star.png}
            \caption{Kite Connects to Highest Distinction Node}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-clique.png}
            \caption{Kite Connects to Moderate Distinction Node}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-peri.png}
            \caption{Kite Connects to Lowest Distinction Node}
            \label{fig:circleweld}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
            \caption{Kite Connects to Moderate Distinction Node}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
            \caption{Kite Connects to Lowest Distinction Node}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
            \caption{HOLD}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
            \caption{HOLD}
            \label{fig:sf}
    \end{subfigure} 
    \caption{Comparison of kite graphs with varying parameters. Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

@@

\subsection{Capital Conversion as Network Integration of Fields}

%Add portion on pop[ culture being a low constraint activity]
%distinction signals position which is why it's so important

One of the problems with the relationship between multiple fields is how capital might be converted between fields. The ``rate'' between fields has always been a matter of confusion because it is difficult to quantify. Yet, it is an essential feature of an individual's navigation between the positional hierarchies of various fields. Seeking to convert a distinct position from one field to a better position in another is a critical strategy in the overall positional portfolio of agents.
